Submission and Formatting Instructions for \\ International Conference on Machine Learning (ICML 2019)

### 2019-04-24 paper/icml_ai4good/main.tex
next intro update

\section{Introduction}
Ending the epidemics of AIDS, tuberculosis, malaria and other infectious diseases by 2030 is a key target by the Good Health & Well-Being section of the UN Sustainable Development Goals. Despite decades of substantial international efforts, malaria still annually kills about a quarter of a million children under the age of 5 in Africa alone.

Malaria can be routinely cured thanks to a variety of medical interventions. 
Issues are further aggravated due to the emergence of parasite resistance to multiple drugs, including artemisinin, or even insecticides.

@@

Even in the absence of political, economic and social constraints, Malaria epidemiology is governed by a complex set of drivers, few of which can be understood in isolation. These include within-host dynamics, population-specific traits and even local geography. Some progress in modeling specific components has been made, such as the parasite life-cycle, transmission vector dynamics and the inter-dependencies between infection rates and vicinity to open water. However, comprehensive modeling of all of these components in a regional context remains challenging, and is greatly impeded by the lack of available field data.

Studying the implications of a diverse set of anti-malaria

All of the above limitations require contemporary malaria epidemiology simulators to employ stochastic modeling techniques, which negotiate data scarcity and model uncertainty through the use of appropriate prior distributions. Simulator calibration then equates to calibrating the

, and, above all, the lack of available field data for calibration,

%parasite life-cycle, transmission vectors, population dynamics and even local geographic circumstances, with policy measures ranging from distribution of mosquito nets to experimental vaccines, requires such simulators to be stochastic. Simulation outcomes thus need to be evaluated on a population of subjects.

>>>>

\section{Introduction}
Ending the epidemics of AIDS, tuberculosis, malaria and other infectious diseases by 2030 is a key target within the Good Health \& Well-Being section of the UN Sustainable Development Goals\cite{}.

In contrast to AIDS, Malaria can be routinely cured thanks to the disposability of a variety of medical interventions. 
Issues are further aggravated due to the increasing emergence of parasite resistance to multiple drugs, including artemisinin, or even insecticides. Hence, despite decades of substantial international efforts, initial hopes of regional elimination or even global eradication have not been met. So difficult is Malaria control that, even today, about a quarter of a million children under the age of 5 succumb to it every year in Africa alone.

@@

Even in the absence of political, economic and social constraints, Malaria epidemiology is governed by a complex set of drivers, few of which can be understood in isolation. These include within-host dynamics, population-specific traits and even local geography. Some progress in modeling specific components has been made, such as the parasite life-cycle, transmission vector dynamics and the inter-dependencies between infection rates and vicinity to open water. However, comprehensive modeling of all of these components in a regional context remains challenging, and is greatly impeded by the lack of available field data for regional calibration. Simulational complexity is further aggravated by considering feedback effects from a large arsenal of anti-malaria interventions, ranging from distribution of mosquito nets, indoor residual spraying and mass drug administration to age-specific vaccinations.

All of the above limitations require contemporary malaria epidemiology simulators to employ stochastic modeling techniques, which negotiate data scarcity and model uncertainty through the use of appropriate prior distributions that can be tuned even from small samples of field data. The population dynamics of groups of typically several thousand hosts are then initialised by sampling from the initial distributionsm, using initial random seeds. Forward simulation then proceeds by rolling out simulation dynamics over time. Policymakers then take interest in comparing simulation outcomes of cherry-picked scenarios and interventions with those of suitably chosen control groups.

Stochastic epidemiology simulators have already proven to be an invaluable tool to policymakers with policy implications that are often counterintuitive yet far-ranging. For example, it has been shown that mass vaccination may be largely ineffective in regions of large transmission rates, but may play a crucial role in areas of low transmittivity.

However valuable forward simulations of epidemiology scenarios are, the holy grail of goal-driven policymaking lies ultimately in the inverse problem: Given a desired outcome, we wish to find the optimal respective intervention policy given a specific regional context. Due to computational constraints, even an approximate search over the whole simulator input space usually proves intractable.

% , and, above all, the lack of available field data for calibration,

% parasite life-cycle, transmission vectors, population dynamics and even local geographic circumstances, with policy measures ranging from distribution of mosquito nets to experimental vaccines, requires such simulators to be stochastic. Simulation outcomes thus need to be evaluated on a population of subjects.
